Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip

### 2014-02-19 PAPER/introduction.tex
English fixes

\section{Background and Contribution}
\label{sec:related_works}
Several works addressed the problem of topology agnostic deadlock
freedom introducing virtual channels~\cite{sancho2002, skeie2002,
skeie2004, koibuchi2003}, but while they show interesting
performances, the low resources available to prevent deadlocks makes them not suitable for
the DNA self-assembled networks we are assuming as
scenario.
Other topology independent algorithms~\cite{schroeder1991,
koibuchi2001, cherkasova1996} do not require any virtual channel but
exploit the concept of ``turn prohibition''.
In particular, authors of~\cite{Patwardhan05evaluatingthe} exploit the creation of a spanning tree of the
topology, placing bidirectional restrictions \hl{by avoiding a packet
to traverse the same link in both up and down directions}.
The hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), but this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches such as
FX~\cite{sancho2000} mitigate this
issue, but the set of turn restrictions is still prefixed
strictly depending on the particular tree root selected. 
Other solutions try to approach the issue of irregular
topologies by limiting the number~\cite{duato1997, gomez2004, koibuchi2008} or the
location~\cite{zhang2008, flich2008, liu2011} of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{constantinides2006, kohler2010,  park2006, ebrahimi2013}.

@@

The \disr{} approach presented in this work is a first attempt to
achieve the same goals of a segment based turn prohibition without
requiring neither the knowledge of a topology graph nor centralized execution. In particular
\disr{} implements segment discovery and turn prohibition using a
completely different mechanism, based on a distributed exchange of
small setup packets requiring on average $15\%$ of the available
resource budget. The following main features distinguish \disr{}
from classic approaches to segment partitioning: 
\begin{itemize}
\item No centralized entity is globally responsible and/or aware of
what is going on, i.e. the status of the \disr{} execution is
collectively distributed among the nodes.
\item  No defect map and/or topology graph is used as input,
thus, the topology has to be discovered \emph{while} segments are
created.
\item At the end of the execution, no segment list is created or
stored anywhere: each node is only aware of belonging to \hl{a segment | some segments},
ignoring the presence of other nodes in the same segment and also the
presence of other segments in the network.
\end{itemize}

>>>>

\section{Background and Contribution}
\label{sec:related_works}
Several works addressed the problem of topology agnostic deadlock
freedom introducing virtual channels~\cite{sancho2002, skeie2002,
skeie2004, koibuchi2003}, but while they show interesting
performances, the low resources available to prevent deadlocks makes them not suitable for
the DNA self-assembled networks we are assuming as
scenario.
Other topology independent algorithms~\cite{schroeder1991,
koibuchi2001, cherkasova1996} do not require any virtual channel but
exploit the concept of ``turn prohibition''.
In particular, authors of~\cite{Patwardhan05evaluatingthe} exploit the creation of a spanning tree of the
topology, placing bidirectional restrictions to avoid that a packet
can traverse a given link in both up and down directions.
The hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), but this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches such as
FX~\cite{sancho2000} mitigate this
issue, but the set of turn restrictions is still prefixed
strictly depending on the particular tree root selected. 
Other solutions try to approach the issue of irregular
topologies by limiting the number~\cite{duato1997, gomez2004, koibuchi2008} or the
location~\cite{zhang2008, flich2008, liu2011} of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{constantinides2006, kohler2010,  park2006, ebrahimi2013}.

@@

The \disr{} approach presented in this work is a first attempt to
achieve the same goals of a segment based turn prohibition without
requiring neither the knowledge of a topology graph nor centralized execution. In particular
\disr{} implements segment discovery and turn prohibition using a
completely different mechanism, based on a distributed exchange of
small setup packets requiring on average $15\%$ of the available
resource budget. The following main features distinguish \disr{}
from classic approaches to segment partitioning: 
\begin{itemize}
\item No centralized entity is globally responsible and/or aware of
what is going on, i.e. the status of the \disr{} execution is
collectively distributed among the nodes.
\item  No defect map and/or topology graph is used as input,
thus, the topology has to be discovered \emph{while} segments are
created.
\item At the end of the execution, no segment list is created or
stored anywhere: each node is only aware of belonging to a segment,
ignoring the presence of other nodes in the same segment and also the
presence of other segments in the network.
\end{itemize}
